---
title: "Expression data from GSE13015 using Bioconductor's ExperimentHub"
author: "Darawan Rinchai"
date: "`r doc_date()`"
vignette: >
  %\VignetteIndexEntry{Expression data from GSE13015 using Bioconductor's ExperimentHub}
  %\VignetteEngine{knitr::rmarkdown}
output: 
  BiocStyle::html_document
---

# Normalized expression data from GSE13015 
Microarray expression matrix platform GPL6106 and clinical data for 67 septicemic patients and made them available as GEO accession [GSE13015](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE13015). GSE13015 data have been parsed into a SummarizedExperiment object available in ExperimentHub
can be used for Differential Expression Analysis, Modular repertiore analysis.

In the below example, we show how one can download this dataset from 
ExperimentHub.

```{r get-expression matrix}
library(ExperimentHub)
dat = ExperimentHub()
res = query(dat , "GSE13015")
temp = hub[["EH5429"]]
data_matrix = assay(temp)
sample_info = data.frame(colData(temp))

```

# sessionInfo()

```{r sessionInfo}
sessionInfo()
```
